---
title: |
  | ASSIGNMENT 1
header-includes: \usepackage{setspace} \onehalfspacing
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1.  X. James Aldrich (u2086396)
2.  Y. Lynn van Oosten  (uXXXXXX)
3.  Z. Diego Araos Munoz (uXXXXXX)

# Theoretical Exercises 
## Solution Theoretical Exercise 1 
a) The estimator $\hat{\mu}=\frac{1}{n+1}\sum_{i=1}^ny_i$ is biased and consistent.
It is biased because $$E[\hat{\mu}]\neq \mu$$

For example:
$$E[\hat{\mu} ]=E[\frac{1}{n+1}\sum_{i=1}^ny_i] =\frac{1}{n+1}\sum_{i=1}^nE[y_i]=\frac{1}{n+1}\sum_{i=1}^n\mu=\frac{n}{n+1}\mu<\mu$$

The estimator is consistent because as n grows arbitrarily large the estimator tends towards the true value.
$$\displaystyle \lim_{n \to \infty} \hat{\mu}=\displaystyle \lim_{n \to \infty}\frac{1}{n+1}\sum_{i=1}^ny_i=\displaystyle \lim_{n \to \infty}\frac{n}{n+1}\displaystyle \lim_{n \to \infty}\frac{\sum_{i=1}^ny_i}{n}=\displaystyle \lim_{n \to \infty}\frac{n}{n+1}\mu=\displaystyle \lim_{n \to \infty}\frac{1}{1+\frac{1}{n}}\mu=\mu 
$$

b)  The estimator $\hat{\mu}=\frac{2}{n}\sum_{i=1}^\frac{n}{2}y_i$ is unbiased and consistent provided n is even.
It is unbiased because $$E[\hat{\mu}]= \mu$$
For example:
$$E[ \hat{\mu} ]=E[\frac{2}{n}\sum_{i=1}^\frac{n}{2}y_i]=\frac{2}{n}\sum_{i=1}^\frac{n}{2}E[y_i]=\frac{2}{n}\sum_{i=1}^\frac{n}{2}\mu=\frac{2}{n}(\frac{n}{2}\mu)=\mu$$
The estimator is consistent when n is even because $$ \frac{n}{2}=m \in N $$ n is shown to be a whole number. The limit of the estimator as n approaches infinity becomes:

$$\displaystyle \lim_{n \to \infty}\hat{\mu}=\displaystyle \lim_{n \to \infty}\frac{2}{n}\sum_{i=1}^\frac{n}{2}y_i=\displaystyle \lim_{m \to \infty}\frac{1}{m}\sum_{i=1}^my_i=\mu$$

c) The estimator is unbiased because: $$ \hat{\mu}=\frac{.1}{100}\sum_{i=1}^{100}y_i+\frac{.9}{n-100}\sum_{i=101}^{n}y_i$$
$$ 
E[\hat{\mu}]=E[\frac{0.1}{100}\sum_{i=1}^{100}y_i]+E[\frac{0.9}{n-100}\sum_{i=101}^{n}y_i]=\frac{0.1}{100}\sum_{i=1}^{100}\mu+\frac{0.9}{n-100}\sum_{i=101}^{n}\mu=\frac{0.1(100)}{100}\mu+\frac{0.9(n-100)}{n-100}=\mu
$$ 
The estimator is consistent because:
$$\displaystyle \lim_{n \to \infty}\hat{\mu}=\displaystyle \lim_{n \to \infty}\frac{.1}{100}\sum_{i=1}^{100}y_i+\frac{.9}{n-100}\sum_{i=101}^{n}y_i=\displaystyle \lim_{m \to \infty}$$


## Solution Theoretical Exercise 2 


# Empirical Exercise

## Solution Empirical Exercise 1
```{r,warn=F}
# NOTE: Use below line to install the package. Remove the line after,
#       as otherwise pdf generation won't work.
# install.packages("mvtnorm") 
library("mvtnorm")
means = c(0,0)
VCOV = matrix(c(1,0,0,1),nrow=2,byrow=T)
n=2
X = rmvnorm(n,mean=means,sigma=VCOV) 
X
```
The function `rmvnorm` draws `n` values from the multivariate distribution, with means given in `means` and the covariance matrix `sigma`.


## Solution Empirical Exercise 2
```{r, fig.height = 3, fig.width = 4, fig.align = "center"}
# Code block generating a plot
# The figure size and positioning can be adjusted in the options for the block
a = runif(10000)
plot(a)
```
And so on and so forth... 

# Some final tips
- Try producing the pdf already while writing. There can be errors, where no pdf file can be produced (e.g. if you don't close close a mathematical expression with `$`). If you produce the pdf after  having written only a small part, and an error occurs, you know in which part the error is. 
- Throughout, keep track of the variables you create, and their dimensions
- If part of your code produces an error, first try to narrow down where the error is coming from by running individual code blocks or lines one by one

