---
title: |
  | ASSIGNMENT XX
header-includes: \usepackage{setspace} \onehalfspacing
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1.  X. James Aldrich (u2086396)
2.  Y. Lynn van Oosten  (uXXXXXX)
3.  Z. Diego Araos Munoz (uXXXXXX)

# Theoretical Exercises 
## Solution Theoretical Exercise 1 
a) 
$$
\boldsymbol{E}[u]
$$

b)  Math can be written like this $y_i = \boldsymbol{x}_i^{\prime} \beta + \varepsilon_i$
c)  or as an equation on its own line: 
$$ 
y_i = \boldsymbol{x}_i^{\prime} \beta + \varepsilon_i
$$ 

## Solution Theoretical Exercise 1 
And so on and so forth....

# Empirical Exercise

## Solution Empirical Exercise 1
```{r,warn=F}
# NOTE: Use below line to install the package. Remove the line after,
#       as otherwise pdf generation won't work.
# install.packages("mvtnorm") 
library("mvtnorm")
means = c(0,0)
VCOV = matrix(c(1,0,0,1),nrow=2,byrow=T)
n=2
X = rmvnorm(n,mean=means,sigma=VCOV) 
X
```
The function `rmvnorm` draws `n` values from the multivariate distribution, with means given in `means` and the covariance matrix `sigma`.


## Solution Empirical Exercise 2
```{r, fig.height = 3, fig.width = 4, fig.align = "center"}
# Code block generating a plot
# The figure size and positioning can be adjusted in the options for the block
a = runif(10000)
plot(a)
```
And so on and so forth... 

# Some final tips
- Try producing the pdf already while writing. There can be errors, where no pdf file can be produced (e.g. if you don't close close a mathematical expression with `$`). If you produce the pdf after  having written only a small part, and an error occurs, you know in which part the error is. 
- Throughout, keep track of the variables you create, and their dimensions
- If part of your code produces an error, first try to narrow down where the error is coming from by running individual code blocks or lines one by one

